A Search for Supernova Remnants in NGC\,6946

### 2018-11-04 ms.tex
Added an abstract

The relatively nearby spiral galaxy NGC6946 is one of the most actively star forming galaxies in the local Universe.
Here we report on an optical search for SNRs

>>>>

The relatively nearby spiral galaxy NGC6946 is one of the most actively star forming galaxies in the local Universe.  Nine supernovae have been observed since 1917 and as a result NGC6946 must contain a large number of SNRs.  Here we report a new optical search for SNRs in NGC6946.  Specifically, we have identified 147 emission nebulae in NGC6946 as likely SNRs based on the fact that they appear to have elevated [SII]:\ha\ ratios compared to HII regions based in narrow band images obtained on WYIN.  We then obtained spectra of ?? of these emission nebulae with Gemini/GMOS; of these ?? have [SII]:\ha\ ratios greater than 0.4, the criterion for establishing an emission nebulae as a SNR optically.  All but one of the 27 SNR candidates identified earlier by Matonick and Fesen are contained in our sample.  However, there is very little overlap in our sample between the SNR candidates identified by Bruursma et al from [Fe II] imagery or by Lacey et al from radio data.  Very few of the SNR candidates are X-ray sources, unlike the situation in some other galaxies such as M33 and M83, possible due to the fact that there is more reddening along the line of sight to NGC6946 than these galaxies.  The emission line ratios, e.g of [N II]:\ha of the candidates in NGC6946 are fairly typical of those observed in SNRs in samples of other galaxies with comparable metallicity.  None of the historical SNe were detected as SNRs and none of the candidates show evidence of anomalous abundances suggestive of ejecta material or  significant velocity broadening in our low resolution spectra.
